Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-12-05 Manuscript/manuscript.tex
Add details of NMR experiments written by Tiago

\subsection{Measurements of acyl chain order parameters}
\todo{SAMULI: Short description about the order parameter experiments by Tiago.}

>>>>

\subsection{Measurements of acyl chain order parameters}
A R-type Proton Detected Local Field (R-PDLF) experiment was performed to determine C--H bond order
parameters, $S_{\rm{CH}}=1/2\langle3cos^2\theta-1\rangle$, where $\theta$ denotes the angle of the C--H bond
with the bilayer normal and the angular brackets define a time average on a time scale of approximately 1 microsecond.
The experiment was done using a Bruker Avance III 400 spectrometer operating at a 1H Larmor frequency of 400.03 MHz
equipped with a standard 4 mm CP-MAS HXY probe. The set up of the R-PDLF experiment was the following
(using the notation as in figures 1c and 2c of the original reference for the R-PDLF
experiment [S. V. Dvinskikh, H. Zimmermann, A. Maliniak and D. Sandström, J. Mag. Res. 168, 194 (2004)]).
The magic angle spinning (MAS) frequency used was 5.15 kHz. The recoupling pulses in the R18 blocks had
therefore a length of 10.79 us which correspond to a nutation frequency of 46.35 kHz. Increments of 18x2 recoupling
pulses where used giving a spectral width of 2.6 kHz in the indirect dimension and a total number of 32 points in
the indirect dimension were recorded. These settings enable to record dipolar slices with a C--H bond order parameter
resolution of +- 0.01. The C--H bond order parameter determined from a given dipolar
splitting, $\Delta\nu$ (see e.g. Figure XX as SI) is equal to $\Delta\nu/(0.315\times21.5 kHz)$, where 0.315 is
the scaling factor of the R18 recoupling sequence and 21.5 kHz is the maximum 1H-13C dipolar coupling for a C--H bond.
The refocused-INEPT transfer [G. Morris and R. Freeman, J. Am. Chem. Soc. 101, 760 (1979); D. Burum, R. Ernst, J. Mag. Res. 39, 163 (1980)]
was used for transferring the polarization from 1H nuclei to the covalently bond 13C nuclei with the delays $\tau_1$ = 1.94 ms and $\tau_2$ = 0.97 ms
(set as multiples of the MAS rotation period). The pulses for the refocused-INEPT sequence had a nutation frequency equal to 63.45 kHz.
For acquiring the spectra, a total number of 1024 transients were recorded for each point in the indirect dimension, using an acquisition time of 0.1 s under SPINAL64 1H decoupling [B. Fung, A. Khitrin, K.Ermolaev, J. Mag. Res. 142, 97 (2000)] with a nutation frequency of 50 kHz, and with dwell time giving a spectral width of 200 ppm for the 13C chemical shift dimension. The set of free induction decays recorded were then processed as described e.g. in [T. M. Ferreira, B. Medronho, R. W. Martin, D. Topgaard, Phys. Chem. Chem. Phys. 10, 6033 (2008)]. For assigning the dipolar splittings in the crowded spectral region between 29 and 30 ppm both the assignments made for POPC in [ T. M. Ferreira, F. Coreta- Gomes, O. H. S. Ollila, M. J. Moreno, W. L. C. Vaz, D. Topgaard, Phys. Chem. Chem. Phys. 15, 1976-1989 (2013)] and the POPS order parameters simulated and reported in this work were taken as a reference.
